\quad \quad Maintenance and support 
requirements address items specific to the ongoing maintenance and support of your 
product after delivery. Think of these requirements as if you were the ones who would 
be responsible for caring for customers/end user after the product is delivered in its 
final form and in use "in the field". What would you require to do this job? Specify 
items such as: where, how and who must be able to maintain the product to correct 
errors, hardware failures, etc.; required support/troubleshooting manuals/guides; 
availability/documentation of source code; related technical documentation that must 
be available for maintainers; specific/unique tools required for maintenance; 
specific software/environment required for maintenance; etc.

\subsection{Register RFID Tag}
\subsubsection{Description}
\quad \quad The system shall allow admin users to register RFID tags and associate those tags 
with students. Whenever introducing a new RFID tag, the admin user will register the 
new tag with the system then associate it with a student in need.
\subsubsection{Source}
\quad \quad CSE Senior Design project specifications
\subsubsection{Constraints}
\quad \quad There are no foreseeable constraints for this requirement  
\subsubsection{Standards}
\quad \quad No specific standards that apply to this requirement
\subsubsection{Priority}
\quad \quad Moderate

\subsection{Administrator Maintainence}
\subsubsection{Description}
\quad \quad The admin shall be able to add staffs who shall be able to login and use the system to 
check out the students. The admin shall have enter all the necessary information of 
the staff who is being added. For security purposee the staffs shall have a secure 
login. furthermore, if new admin needs to added, the existing admin can allow or 
disallow the school staff to be the admin. 
\subsubsection{Source}
\quad \quad Product customer
\subsubsection{Constraints}
\quad \quad The system shall allow admins to add new users.
\subsubsection{Standards}
\quad \quad At this moment team is not aware about the standards with this requirements.
\subsubsection{Priority}
\quad \quad High

