\quad \quad Performance requirements 
address items such as: how fast specific critical operations must complete; how long 
it takes to start/stop activities; how long the battery must last; maximum time it 
must take to set up; etc.

\subsection{Quick RFID Detection}
\subsubsection{Description}
\quad \quad When the scanner detects any RFID tags around , it sends signal to the application. 
The application should then display the name and image of a student who is linked to 
that RFID tag. This entire seconds should be done under 2 seconds once the scanner 
reads a tag.
\subsubsection{Source}
\quad \quad CSE Senior Design project specifications
\subsubsection{Constraints}
\quad \quad RFID API connection
\subsubsection{Standards}
\quad \quad No specific standards that apply to this requirement
\subsubsection{Priority}
\quad \quad High

\subsection{Maximum RFID Tag Detection Error Rate}
\subsubsection{Description}
\quad \quad The system shall not throw out any undesired error while it is in operation. Testing 
shall be performed with deep caution by the team and the errors that might take place 
should be less that 2 percentage. 
\subsubsection{Source}
\quad \quad Product customer
\subsubsection{Constraints}
\quad \quad The system shall be error free	.
\subsubsection{Standards}
\quad \quad At this moment team is not aware about the standards with this requirements.
\subsubsection{Priority}
\quad \quad Medium

\subsection{RFID Tag Extraction}
\subsubsection{Description}
\quad \quad The system shall be able to extract the RFID number from the RFID Tags example, 
windshield stickers and Cards.
\subsubsection{Source}
\quad \quad other requirerments
\subsubsection{Constraints}
\quad \quad RFID shall extract the tags and it is one of the main constrainsts for this project.
\subsubsection{Standards}
\quad \quad At this moment team is not aware about the standards with this requirements.
\subsubsection{Priority}
\quad \quad Critical