\quad \quad Safety requirements might 
address items specific to your product such as: no exposure to toxic chemicals; lack 
of sharp edges that could harm a user; no breakable glass in the enclosure; no direct 
eye exposure to infrared/laser beams; packaging/grounding of electrical connections to 
avoid shock; etc.

\subsection{Log Responsible Staff Member}
\subsubsection{Description}
\quad \quad After the student has been checked out or cleared by the school staff, that 
information need to be updated in the system. The time of check in or check out 
should be correclty entered for the security of the student.
\subsubsection{Source}
\quad \quad Product customer
\subsubsection{Constraints}
\quad \quad The system shall correctly log the information.
\subsubsection{Standards}
\quad \quad At this moment team is not aware about the standards with this requirements.
\subsubsection{Priority}
\quad \quad High

\subsection{Weatherproof System}
\subsubsection{Description}
\quad \quad As the RFID reader need to scan the cars that will all be done outdoors. Due to the 
\quad \quad bi-polar weather here in Texas, the system shall be weather proof such as water proof, 
heat resistant and wind proof.
\subsubsection{Source}
\quad \quad Product customer
\subsubsection{Constraints}
\quad \quad The system shall with stand normal texas weather.
\subsubsection{Standards}
\quad \quad At this moment team is not aware about the standards with this requirements.
\subsubsection{Priority}
\quad \quad Medium

