\quad \quad In this section, all of the various artifacts that are to be generaterated and 
maintained are described.

\subsection{Project Charter}
\quad \quad The Project Charter is this document. It will be updated as major changes are 
updated, and will provide a guiding backbone for the progress of this project.

\subsection{Product Backlog}
\quad \quad As product gets backlog, more manhours will be applied in importance order. This 
form will be used to designate what was expected to be accomplished, yet was not 
completed.

\subsection{Sprint Planning}
\quad \quad Sprints will be planned with all team members present at the beginning of all 
sprints. Changes to the expectations to a sprint will take place with at least a 
majority in concensus.

\subsubsection{Sprint Goal}
\quad \quad Sprint goals will generated during planning and rechecked before the end of each 
sprint. Failing to complete all tasks for a sprint goal will cause reevaluation of 
future deadlines and will be tracked in the product backlog.

\subsubsection{Sprint Backlog}
\quad \quad Sprint Backlogs will be re-evaluated and worthwhile actions will be added to 
subsequent sprints.

\subsubsection{Task Breakdown}
\quad \quad Tasks will be divided to each team member's specialities. Free members will be 
applied to Tasks overlapping or concurrent to busy team members.


\subsection{Sprint Retrospective}
\quad \quad Activities done during sprints will be reviewed and successful activites will be 
promoted to be attempted again. The retrospective will be a time of communication 
and free flowing of ideas.

\subsection{Individual Status Reports}
\quad \quad Individual Status Reports will be generated by each team member.

\subsection{Engineering Notebooks}
\quad \quad Engineering Notebooks will be kept by all team members and checked as needed to 
remain in regulation. Each team member is free to fill their notebook with relevant 
figures and information to complete their tasks.

\subsection{Closeout Materials}
\quad \quad Closeout Materials will we generated before the completion of the project. These 
materials include a \"How To demo\", product website, a product poster, and a video 
of use.

\subsubsection{System Prototype}
\quad \quad A working System Prototype will be implimented before May 2018.

\subsubsection{Project Poster}
\quad \quad A detailed Project Poster will be created before May 2018.

\subsubsection{Web Page}
\quad \quad A Web Page documenting the design process and related material may be created before 
May 2018.

\subsubsection{Demo Video}
\quad \quad A Demo Video will be created, showing the product in action, before May 2018.

\subsubsection{Source Code}
\quad \quad Source Code will be hosted on GitHub.

\subsubsection{Source Code Documentation}
\quad \quad Source Code Documentation will be taken care of by Doxygen.

\subsubsection{Hardware Schematics}
\quad \quad Hardware Schematics will be maintained as hardware is purchased or manufactured. 
These will be available upon project completion.

\subsubsection{CAD files}
\quad \quad CAD files will be hosted on GitHub.

\subsubsection{Installation Scripts}
\quad \quad Installation Scripts will be installed to hardware before reaching the site.

\subsubsection{User Manual}
\quad \quad A User Manual will be created and either available on the website or in physical copy.